How to compute the fusion product of MV cycles in type A

### 2021-04-08 draft.tex
zzzzz...

\subsection{Some subvarieties of affine Grassmannians}
Now fix effective dominant coweights $\lambda', \lambda'' \in P_{++}$ of sizes $N',N''$  and their sums $ \lambda = \lambda' + \lambda'' $ of size $ N = N'+N''$. 
% Coweights define elements in the various affine Grassmannians which we consider. Warning: We will write only coset representatives for elements of the various Grassmannians; we hope that it is evident which right cosets they represent. 
% the right cosets which they represent are clear from the context.
We consider the following subschemes of the affine Grassmannians.
% 
\begin{definition}
The \textbf{spherical Schubert cell} $\Gr^\lambda = G(\cO) t^\lambda$ and its closure 
    $ \overline\Gr^\lambda = \bigcup_{\lambda' \le \lambda} \Gr^{\lambda'} $.  
\end{definition}
    % \acom{do we prefer $\overline{\Gr}^\lambda$ to $\overline{\Gr^\lambda}$? I am for the former! Though it is less accurate??} \jcom{I'm not sure which is better.  I was ``testing'' it out.}
    Since $ \lambda $ effective, $ t^\lambda \in \Gr^+ $ and so the spherical Schubert variety $\overline{\Gr}^\lambda $ lies inside the positive part $ \Gr^+$ of the affine Grassmannian.
    % 
\begin{definition} 
    The \textbf{fusion of two spherical Schubert varieties} $$ \overline{\Gr}^{\lambda', \lambda''}_{0, \AA} = \overline{\Gr}^{\lambda'} \ast_\AA \overline{\Gr}^{\lambda''} \rightarrow \AA $$
\end{definition}
    % \acom{I guess that it is good to have the notation here, in place of $\overline{\overline\Gr^{\lambda'}\times\overline\Gr^{\lambda''}\times\AA^\times}$..}
    %\acom{should we also subsript this family with $0,\AA$?}
    By construction the fibre $ \overline{\Gr}_{0,s}^{\lambda', \lambda''} $ over $ s \ne 0 $ is $ \overline{\Gr}^{\lambda'} \times \overline{\Gr}^{\lambda''}$.  
    % By \cite[Proposition 3.1.14]{zhu2016introduction},
    % Zhu's theorem (\jcom{need ref} \acom{pretty sure it's }), 
    % the fibre over $ 0 $ is $ \overline{\Gr}^{\lambda' + \lambda''}$.
    Over $s=0$ the fibre is $ \overline{\Gr}^{\lambda' + \lambda''}$ (and reduced) by 
    % a theorem of Zhu 
    \cite[Proposition 3.1.14]{zhu2016introduction}.

@@

Now fix two effective coweights $ \mu', \mu'' \in \mathbb N^m$ such that $ \mu_i$ has size $ N_i$ and such that $ \mu = \mu' + \mu'' $ is dominant.  (We do not require $ \mu', \mu'' $ to be effective.) Using $ \mu, \mu', \mu''$, we define the following subschemes.

@@

    \item Fix the ``$\mu$-numeration'' \((e^1_1,\ldots,e^{\mu_1}_1,\ldots,e^1_m,\ldots,e^{\mu_m}_m)\) of the standard basis of $\CC^N$. The Mirkovic--Vybornov slice $\TT_\mu$ is defined as the set of $A\in M_N(\CC)$ such that 
    \[
        \begin{aligned}
            &\text{for all } 1 \le a,s\le m\,,
            \text{for all } 1\le b\le \mu_a\,, 1\le t\le \mu_s\,, \\
            &\text{if } 1\le t < \mu_s \text{ or } t = \mu_s < b \le \mu_a \\
            &\text{then } (e^t_s)' (A-J_\mu) e^b_a = 0 \,.
        \end{aligned}    
    \]
    In words, $A$ is a $\mu$ Jordan form matrix plus a $\mu\times\mu$ block matrix with possibly nonzero entries occuring in the first $\min(\mu_i,\mu_j)$ columns of the last row of each $\mu_i\times\mu_j$ block. 
    % $\dim \TT_\mu = N^2 - \dim \OO_\mu$. 
    In pictures, aka by example, the elements $A$ for $\mu=(3,2,2,1)$ look like 
    \[
        \left[\begin{BMAT}(e){ccc;cc;c;c}{ccc;cc;c;c}
             & 1 & & & & & \\
             &  & 1 & & & & \\
            A_{11}^1 & A_{11}^2 & A_{11}^3 & A_{12}^1 & A_{12}^2 & A_{13}^1 & A_{14}^1 \\
              &  & &  & 1 & & \\
              A_{21}^1 & A_{21}^2 & & A_{22}^1 & A_{22}^2 & A_{23}^1 & A_{24}^1 \\
             A_{31}^1 & & & A_{32}^1 & & A_{33}^1 & A_{34}^1 \\
             A_{41}^1 & & & A_{42}^1 & & A_{43}^1 & A_{43}^1
        \end{BMAT}
        \right]
    \]
    Smaller: 
    \[
        \left[\begin{BMAT}(e){ccc;cc}{ccc;cc} 
            0 & 1 & 0 & 0 & 0\\
            0 & 0 & 1 & 0 & 0\\
            A_{11}^1 & A_{11}^2 & A_{11}^3 & A_{12}^1 & A_{12}^2\\
            0 & 0 & 0 & 0 & 1\\
            A_{21}^1 & A_{21}^2 & 0 & A_{22}^1 & A_{22}^2
            \end{BMAT}\right]    
            \mapsto 
            \left[\begin{array}{rr}
                t^{3} - A_{11}^3 t^2 - A_{11}^2 t - A_{11}^1 & -A_{21}^2 - A_{21}^1  \\
                -A_{12}^2 t - A_{12}^1 & t^{2} - A_{22}^2 t - A_{22}^1
            \end{array}\right]
    \]

@@

    \item The ``upper-triangular'' \mvy slice $\UU^{\mu', \mu''}_{0,\AA}\rightarrow \AA $, defined by
    $$
    \UU^{\mu', \mu''}_{0,\AA} := \{ (A,s) \in \TT_\mu \times \AA : g(A)_{ii} = t^{\mu_{1,i}} (t-s)^{\mu_{2,i}}, g(A)_{ij} = 0 \text{ for $ j < i $ }\}
    $$
    So a matrix in $\UU^{\mu', \mu''}_{0,\AA}$ is weakly block upper-triangular and its diagonal blocks are given by the companion matrices for the polynomials $t^{\mu_{1,i}} (t-s)^{\mu_{2,i}}$ ($i=1,\dots,m$).

@@

    $\UU_{0,0}$ entries look like 
    \[
        \left[\begin{BMAT}(e){ccc;cc}{ccc;cc} 
            0 & 1 & 0 & 0 & 0\\
            0 & 0 & 1 & 0 & 0\\
            0 & 0 & 0 & A_{12}^1 & A_{12}^2\\
            0 & 0 & 0 & 0 & 1\\
            0 & 0 & 0 & 0 & 0
            \end{BMAT}\right]    
            % \mapsto 
            % \left[\begin{array}{rr}
            %     t^{3} & 0 \\
            %     -A_{12}^2 t - A_{12}^1 & t^{2}
            % \end{array}\right]
    \]
    $\UU^{\mu', \mu''}_{0,\AA}$ entries look like 
    \[
        \left[\begin{BMAT}(e){ccc;cc;c}{ccc;cc;c} 
            0 & 1 & 0 & 0 & 0 & 0\\
            0 & 0 & 1 & 0 & 0 & 0\\
            0 & -s^2 & 2s & A_{12}^1 & A_{12}^2 & A_{13}^1 \\
            0 & 0 & 0 & 0 & 1 & 0\\
            0 & 0 & 0 & 0 & s & A_{23}^1\\
            0 & 0 & 0 & 0 & 0 & s
            \end{BMAT}\right]    \in \UU_{0,s}^{(1,1,0),(2,1,1)}
    \]

@@

\begin{proof}
    Let $ A \in \overline{\OO_{\lambda_1,\lambda_2}}\cap\TT_{\mu_1,\mu_2}^+$ and let $ g $ be the polynomial matrix formed by the Mirkovic-Vybornov isomorphism.  Then the diagonal entries of $ g $ are $ t^{\mu_{1,k}} (t-s)^{\mu_{2,k}}$ and we can factor
    $$ g = (g t^{-\mu_1}(t-s)^{-\mu_2}) t^{\mu_1}(t-s)^{\mu_2} \in N[t, t^{-1}, (t-s)^{-1}] t^{\mu_1} (t-s)^{\mu_2}$$
    So we get containment in one direction.

    For the reverse containment, we choose $ [g] \in \overline{(\Grbd[2])^{\lambda_1,\lambda_2}}\cap S_{\mu_1,\mu_2}$.  By the lemma below, $[g] \in \cW_\mu$ and thus it lies in the image of our map and we are done.
\end{proof}

% Define $S_{\mu_1,\mu_2}^s = N_-\xT[t^{-1}] t^{\mu_1} (t-s)^{\mu_2}$.

\acom{is it a fibre of $S_{\mu_1,\mu_2}$ defined above?}

@@

\begin{lemma}%[Roger's lemma]
    Let $\mu_1,\mu_2$ be dominant and let $s\in \AA^1 - \{0\}$. Then 
    \begin{equation}
        S_{\mu_1,\mu_2}^s \subset \cW_\mu 
    \end{equation}
    where $\mu = \mu_1 + \mu_2$.
\end{lemma}

@@

\begin{proposition}(\cite{baumann2019mirkovic})
    % Given two MV cycles $Z_\tau$ and $Z_\sigma$ of type\dots 
    Let $Z_{i} = Z_{\tau_i}$  be an MV cycle of type $\lambda_i\in P_{++}$ and weight $\mu_i\in P$ ($i = 1,2$). Then 
    \begin{equation}
        % Z_\tau\ast Z_\sigma 
        m_{\lambda_1\lambda_2} ([Z_1]\otimes[Z_2]) 
        = 
        % \sum_{Z\in\cZ(\lambda)_\mu} 
        \sum_{\tau\in S(\lambda)_\mu}
        i\left(
            Z_\tau, Z_1\circ Z_2 
            % \pi^{-1}(0)\cdot\overline{Z_1\times Z_2\times U}
        \right) [Z_\tau]
    \end{equation}
    and the intersection multiplicities on the right are found by the algorithm described in APX.
    In particular, 
    the multiplicity of $Z_\tau$
    % in the product of the zero fiber 
    % (divisor class) 
    % and the 
    % (Zariski) 
    % closure of the family $Z_1 \times Z_2 \times U$ 
    is equal to the multiplicity of its generalized orbital variety $X_\tau$ among the set 
    \begin{equation}\label{eq:tabmult}
        \irr\lim_{s\to 0} \overline{\OO}^{\lambda_1,\lambda_2}_{0,s}\cap\UU^{\mu_1,\mu_2}_{0,s} \,. 
        % \irr \lim_{s\to 0} \overline\OO^s_{\lambda_1,\lambda_2} \cap \TT_{\mu_1,\mu_2}^{+,s}
    \end{equation}
    Since stable MV cycles can be represented by ordinary ones the multiplicities in 
    $$
    b_{Z_1}b_{Z_2} = \sum_{Z\in\cZ(\infty)_{-\nu_1 - \nu_2}} i \left(
        Z, Z_1 \circ Z_2 
        % \pi^{-1}(0) \cdot \overline{Z_1 \times Z_2 \times U}
    \right) b_Z 
    $$
    can also be deduced from \cref{eq:tabmult} for appropriate choices of $\lambda_i$ and $\mu_i$ ($i = 1,2$).
\end{proposition}
\acom{or Corollary?}

@@

\begin{proposition}
    Let $\tau_1,\tau_2$\dots 
    \[
    \{A\in\UU_{0,s}^{\mu_1,\mu_2} : A \big|_{\mu^1 + \cdots + \mu^i} \in \OO_{0,s}^{\lambda_{1}^{(i)},\lambda_2^{(i)}} \text{ all } i\} = Z_{\tau_1}\times Z_{\tau_2}
    \]
\end{proposition}

@@

    The left hand side is the same thing as
    $$ \CC\xt^m / (L \otimes_{\CC[t]} \CC\xt) = (\CC[t]^m/L) \otimes_{\CC[t]} \CC\xt $$
    \acom{Restricting to an eigenspace is like inverting (forgetting) the action of $t$ by any other generalized eigenvalue. Does this have to do with the fact that a functor $F: \sch \to \set$ commutes with projective limit if and only if it's representable?}

@@

\begin{question}[Related question]
    If $\mu_1,\mu_2$ are not dominant, the LHS is smaller so the map $?$ has no chance of being an isomorphism. In general the map $?$ has to do with producing a matrix from a linear operator. 
    \[
    \begin{tikzcd}
        \overline\Gr^{\lambda_1,\lambda_2}_{0,s}\cap S^{\mu_1,\mu_2}_{0,s} \ar[r,equals]\ar[d] & \overline\Gr^{\lambda_1} \cap S^{\mu_1} \times \overline\Gr^{\lambda_2} \cap S^{\mu_2} \supset Z_1 \times Z_2 \ar[d]\\
        \overline\OO^{\lambda_1,\lambda_2}_{0,s} \cap \UU^{\mu_1,\mu_2}_{0,s} \ar[r,"?"] & \overline\OO^{\lambda_1}\cap \TT_{\mu_1}\cap \n \times \overline\OO^{\lambda_2}\cap \TT_{\mu_2}\cap \n
    \end{tikzcd}    
    \]
\end{question}

@@

\begin{example}
Let $G = SL_3$ and consider the tableaux
$$\tau_1 = \young(12,3) \hspace{.5cm} \text{ and } \hspace{.5cm} \tau_2=\young(13,2).$$
The MV cycles corresponding to $\tau_1$ and $\tau_2$ are both isomorphic to $\PP^2$.
The weights are $\lambda_1 = \lambda_2 = (2,1,0)$ and $\mu_1 = \mu_2 = (1,1,1)$. Hence the matrix in consideration is 
\[
X = \left[\begin{BMAT}(e){cc;cc;cc}{cc;cc;cc}
    0 & 1 & & & & \\
     & s & a_1 & a_2 & b_1 & b_2 \\
     & & 0 & 1 & & \\
     & & & s & b_3 & b_4 \\
     & & & & 0 & 1 \\
     & & & & & s
\end{BMAT}
\right].
\]

>>>>

\subsection{Some subvarieties of affine Grassmannians}
Now fix effective dominant coweights $\lambda', \lambda'' \in P_{++}$ of sizes $N',N''$  and their sums $ \lambda = \lambda' + \lambda'' $ of size $ N = N'+N''$. 
% Coweights define elements in the various affine Grassmannians which we consider. Warning: We will write only coset representatives for elements of the various Grassmannians; we hope that it is evident which right cosets they represent. 
% the right cosets which they represent are clear from the context.
We consider the following subschemes of the affine Grassmannians.
% 
\begin{definition}
    The \textbf{spherical Schubert cell} $\Gr^\lambda = G(\cO) t^\lambda$ and its closure 
    $ \overline\Gr^\lambda = \bigcup_{\lambda' \le \lambda} \Gr^{\lambda'} $ a \textbf{spherical Schubert variety}.  
\end{definition}
    % \acom{do we prefer $\overline{\Gr}^\lambda$ to $\overline{\Gr^\lambda}$? I am for the former! Though it is less accurate??} \jcom{I'm not sure which is better.  I was ``testing'' it out.}
    Note, since $ \lambda $ is effective, $ t^\lambda \in \Gr^+ $ and so the spherical Schubert variety $\overline{\Gr}^\lambda $ lies inside the positive part $ \Gr^+$ of the affine Grassmannian. \acom{why and so? cuz orbits are connected?}
    % 
\begin{definition} 
    The \textbf{fusion of two spherical Schubert varieties} 
    $$ 
    \overline{\Gr}^{\lambda', \lambda''}_{0, \AA} = \overline{\Gr}^{\lambda'} \ast_\AA \overline{\Gr}^{\lambda''} \rightarrow \AA \,.
    $$
\end{definition}
    % \acom{I guess that it is good to have the notation here, in place of $\overline{\overline\Gr^{\lambda'}\times\overline\Gr^{\lambda''}\times\AA^\times}$..}
    %\acom{should we also subsript this family with $0,\AA$?}
    By construction the fibre $ \overline{\Gr}_{0,s}^{\lambda', \lambda''} $ for $ s \ne 0 $ is $ \overline{\Gr}^{\lambda'} \times \overline{\Gr}^{\lambda''}$.  
    % By \cite[Proposition 3.1.14]{zhu2016introduction},
    % Zhu's theorem (\jcom{need ref} \acom{pretty sure it's }), 
    % the fibre over $ 0 $ is $ \overline{\Gr}^{\lambda' + \lambda''}$.
    Over $s=0$ the fibre is $ \overline{\Gr}^{\lambda' + \lambda''}$ (and reduced) by 
    % a theorem of Zhu 
    \cite[Proposition 3.1.14]{zhu2016introduction}.

@@

Now fix two effective coweights $ \mu', \mu'' \in \mathbb N^m$ of size $N',N''$ resp. such that $ \mu = \mu' + \mu'' $ is dominant. (We do not require $ \mu', \mu'' $ to be effective.) 
Using $ \mu, \mu', \mu''$, we define the following subschemes.

@@

    \item Fix the ``$\mu$-numeration'' \((e^1_1,\ldots,e^{\mu_1}_1,\ldots,e^1_m,\ldots,e^{\mu_m}_m)\) of the standard basis of $\CC^N$. The Mirkovic--Vybornov slice $\TT_\mu$ is defined as the set of $A\in M_N(\CC)$ such that 
    \[
        \begin{aligned}
            &\text{for all } 1 \le a,s\le m\,,
            \text{for all } 1\le b\le \mu_a\,, 1\le t\le \mu_s\,, \\
            &\text{if } 1\le t < \mu_s \text{ or } t = \mu_s < b \le \mu_a \\
            &\text{then } e^t_s\cdot (A-J_\mu) e^b_a = 0 \,.
        \end{aligned}    
    \]
    In words, $A$ is a $\mu$ Jordan form matrix plus a $\mu\times\mu$ block matrix with possibly nonzero entries occuring in the first $\min(\mu_i,\mu_j)$ columns of the last row of each $\mu_i\times\mu_j$ block. 
    % $\dim \TT_\mu = N^2 - \dim \OO_\mu$. 
    In pictures, aka by example, the elements $A$ for $\mu=(3,2,2,1)$ look like 
    \[
        \left[\begin{BMAT}(e){ccc;cc;c;c}{ccc;cc;c;c}
             & 1 & & & & & \\
             &  & 1 & & & & \\
            A_{11}^1 & A_{11}^2 & A_{11}^3 & A_{12}^1 & A_{12}^2 & A_{13}^1 & A_{14}^1 \\
              &  & &  & 1 & & \\
              A_{21}^1 & A_{21}^2 & & A_{22}^1 & A_{22}^2 & A_{23}^1 & A_{24}^1 \\
             A_{31}^1 & & & A_{32}^1 & & A_{33}^1 & A_{34}^1 \\
             A_{41}^1 & & & A_{42}^1 & & A_{43}^1 & A_{43}^1
        \end{BMAT}
        \right]
    \]
    Smaller: 
    \[
        \left[\begin{BMAT}(e){ccc;cc}{ccc;cc} 
            0 & 1 & 0 & 0 & 0\\
            0 & 0 & 1 & 0 & 0\\
            A_{11}^1 & A_{11}^2 & A_{11}^3 & A_{12}^1 & A_{12}^2\\
            0 & 0 & 0 & 0 & 1\\
            A_{21}^1 & A_{21}^2 & 0 & A_{22}^1 & A_{22}^2
            \end{BMAT}\right]    
            \mapsto 
            \left[\begin{array}{rr}
                t^{3} - A_{11}^3 t^2 - A_{11}^2 t - A_{11}^1 & -A_{21}^2 - A_{21}^1  \\
                -A_{12}^2 t - A_{12}^1 & t^{2} - A_{22}^2 t - A_{22}^1
            \end{array}\right]
    \]

@@

    \item The ``upper-triangular'' \mvy slice $\UU^{\mu', \mu''}_{0,\AA}\rightarrow \AA $, defined by
    $$
    \UU^{\mu', \mu''}_{0,\AA} := \{ (A,s) \in \TT_\mu \times \AA : g(A)_{ii} = t^{\mu'_{i}} (t-s)^{\mu''_{i}}, g(A)_{ij} = 0 \text{ for $ j < i $ }\}
    $$
    So a matrix in $\UU^{\mu', \mu''}_{0,\AA}$ is weakly block upper-triangular and its diagonal blocks are given by the companion matrices for the polynomials $t^{\mu'_{i}} (t-s)^{\mu''_{i}}$ ($i=1,\dots,m$).

@@

    $\UU_{0,0}^{(?),(?)}$ entries look like 
    \[
        \left[\begin{BMAT}(e){ccc;cc}{ccc;cc} 
            0 & 1 & 0 & 0 & 0\\
            0 & 0 & 1 & 0 & 0\\
            0 & 0 & 0 & A_{12}^1 & A_{12}^2\\
            0 & 0 & 0 & 0 & 1\\
            0 & 0 & 0 & 0 & 0
            \end{BMAT}\right]    
            % \mapsto 
            % \left[\begin{array}{rr}
            %     t^{3} & 0 \\
            %     -A_{12}^2 t - A_{12}^1 & t^{2}
            % \end{array}\right]
    \]
    $\UU^{\mu', \mu''}_{0,\AA}$ entries look like 
    \[
        \left[\begin{BMAT}(e){ccc;cc;c}{ccc;cc;c} 
            0 & 1 & 0 & 0 & 0 & 0\\
            0 & 0 & 1 & 0 & 0 & 0\\
            0 & -s^2 & 2s & A_{12}^1 & A_{12}^2 & A_{13}^1 \\
            0 & 0 & 0 & 0 & 1 & 0\\
            0 & 0 & 0 & 0 & s & A_{23}^1\\
            0 & 0 & 0 & 0 & 0 & s
            \end{BMAT}\right]    \in \UU_{0,s}^{(1,1,0),(2,1,1)}
    \]

@@

\begin{proof}
    Let $ A \in \overline{\OO_{\lambda_1,\lambda_2}}\cap\TT_{\mu',\mu''}^+$ and let $ g $ be the polynomial matrix formed by the Mirkovic-Vybornov isomorphism.  Then the diagonal entries of $ g $ are $ t^{\mu_{1,k}} (t-s)^{\mu_{2,k}}$ and we can factor
    $$ g = (g t^{-\mu_1}(t-s)^{-\mu_2}) t^{\mu_1}(t-s)^{\mu_2} \in N[t, t^{-1}, (t-s)^{-1}] t^{\mu_1} (t-s)^{\mu_2}$$
    So we get containment in one direction.

    For the reverse containment, we choose $ [g] \in \overline{(\Grbd[2])^{\lambda_1,\lambda_2}}\cap S_{\mu',\mu''}$.  By the lemma below, $[g] \in \cW_\mu$ and thus it lies in the image of our map and we are done.
\end{proof}

% Define $S_{\mu',\mu''}^s = N_-\xT[t^{-1}] t^{\mu_1} (t-s)^{\mu_2}$.

\acom{is it a fibre of $S_{\mu',\mu''}$ defined above?}

@@

\begin{lemma}%[Roger's lemma]
    Let $\mu',\mu''$ be dominant and let $s\in \AA^1 - \{0\}$. Then 
    \begin{equation}
        S_{\mu',\mu''}^s \subset \cW_\mu 
    \end{equation}
    where $\mu = \mu_1 + \mu_2$.
\end{lemma}

@@

\begin{proposition}(\cite{baumann2019mirkovic})
    % Given two MV cycles $Z_\tau$ and $Z_\sigma$ of type\dots 
    Let $Z_{i} = Z_{\tau_i}$  be an MV cycle of type $\lambda_i\in P_{++}$ and weight $\mu_i\in P$ ($i = 1,2$). Then 
    \begin{equation}
        % Z_\tau\ast Z_\sigma 
        m_{\lambda_1\lambda_2} ([Z_1]\otimes[Z_2]) 
        = 
        % \sum_{Z\in\cZ(\lambda)_\mu} 
        \sum_{\tau\in S(\lambda)_\mu}
        i\left(
            Z_\tau, Z_1\circ Z_2 
            % \pi^{-1}(0)\cdot\overline{Z_1\times Z_2\times U}
        \right) [Z_\tau]
    \end{equation}
    and the intersection multiplicities on the right are found by the algorithm described in APX.
    In particular, 
    the multiplicity of $Z_\tau$
    % in the product of the zero fiber 
    % (divisor class) 
    % and the 
    % (Zariski) 
    % closure of the family $Z_1 \times Z_2 \times U$ 
    is equal to the multiplicity of its generalized orbital variety $X_\tau$ among the set 
    \begin{equation}\label{eq:tabmult}
        \irr\lim_{s\to 0} \overline{\OO}^{\lambda_1,\lambda_2}_{0,s}\cap\UU^{\mu',\mu''}_{0,s} \,. 
        % \irr \lim_{s\to 0} \overline\OO^s_{\lambda_1,\lambda_2} \cap \TT_{\mu',\mu''}^{+,s}
    \end{equation}
    Since stable MV cycles can be represented by ordinary ones the multiplicities in 
    $$
    b_{Z_1}b_{Z_2} = \sum_{Z\in\cZ(\infty)_{-\nu_1 - \nu_2}} i \left(
        Z, Z_1 \circ Z_2 
        % \pi^{-1}(0) \cdot \overline{Z_1 \times Z_2 \times U}
    \right) b_Z 
    $$
    can also be deduced from \cref{eq:tabmult} for appropriate choices of $\lambda_i$ and $\mu_i$ ($i = 1,2$).
\end{proposition}
\acom{or Corollary?}

@@

\begin{proposition}
    Let $\tau_1,\tau_2$\dots 
    \[
    \{A\in\UU_{0,s}^{\mu',\mu''} : A \big|_{\mu^1 + \cdots + \mu^i} \in \OO_{0,s}^{\lambda_{1}^{(i)},\lambda_2^{(i)}} \text{ all } i\} = Z_{\tau_1}\times Z_{\tau_2}
    \]
\end{proposition}

@@

    The left hand side is the same thing as
    $$ \CC\xt^m / (L \otimes_{\CC[t]} \CC\xt) = (\CC[t]^m/L) \otimes_{\CC[t]} \CC\xt $$
    \acom{Unrelated comments. 1) Restricting to an eigenspace is like inverting (forgetting) the action of $t$ by any other generalized eigenvalue. 2) Does this have to do with the fact that a functor $F: \sch \to \set$ commutes with projective limit if and only if it's representable?}

@@

\begin{question}[Related question]
    If $\mu',\mu''$ are not dominant, the LHS is smaller so the map $?$ has no chance of being an isomorphism. In general the map $?$ has to do with producing a matrix from a linear operator. 
    \[
    \begin{tikzcd}
        \overline\Gr^{\lambda_1,\lambda_2}_{0,s}\cap S^{\mu',\mu''}_{0,s} \ar[r,equals]\ar[d] & \overline\Gr^{\lambda_1} \cap S^{\mu_1} \times \overline\Gr^{\lambda_2} \cap S^{\mu_2} \supset Z_1 \times Z_2 \ar[d]\\
        \overline\OO^{\lambda_1,\lambda_2}_{0,s} \cap \UU^{\mu',\mu''}_{0,s} \ar[r,"?"] & \overline\OO^{\lambda_1}\cap \TT_{\mu_1}\cap \n \times \overline\OO^{\lambda_2}\cap \TT_{\mu_2}\cap \n
    \end{tikzcd}    
    \]
\end{question}

@@

\begin{example}
Let $G = \GL_3$ and consider the tableaux
$$\tau_1 = \young(12,3) \hspace{.5cm} \text{ and } \hspace{.5cm} \tau_2=\young(13,2).$$
The MV cycles corresponding to $\tau_1$ and $\tau_2$ are both isomorphic to $\PP^2$.
The weights are $\lambda_1 = \lambda_2 = (2,1,0)$ and $\mu_1 = \mu_2 = (1,1,1)$. Hence the matrix in consideration is 
\[
X = \left[\begin{BMAT}(e){cc;cc;cc}{cc;cc;cc}
    0 & 1 & & & & \\
     & s & a_1 & a_2 & b_1 & b_2 \\
     & & 0 & 1 & & \\
     & & & s & b_3 & b_4 \\
     & & & & 0 & 1 \\
     & & & & & s
\end{BMAT}
\right].
\]
